~\\[1in] % hack to put space at top.
\textbf{\Huge Acknowledgments}\\

Before mentioning the people who contributed the most to the completion of this thesis, I must thank Columbia University and the National Science Foundation for providing the funding that supported me during my graduate study.

I thank my advisor, Brad Johnson, who advocated for me as a prospective student with an unlikely background, provided essential support and advice throughout my time at Columbia, and steered my projects and papers with a firm hand.

The research that makes up this thesis involved contributions from many external collaborators.
Much of what I know about kinetic inductance detectors I learned from Jonas Zmuidzinas, Peter Day, and Phil Mauskopf. 
It has been fun to work with Kent Irwin, Sherry Cho, Dale Li, and Yanru Song on the multichroic detector development, and I thank them for the fabrication work that allowed me to finish the final piece of this thesis just in time.
I also thank Sean Bryan, George Che, Chris Groppi, Harshad Surdi, Matt Underhill, Rahul Datta, and Jeff McMahon, who all contributed significantly to this project.
Peter Ade, Simon Doyle, Rick LeDuc, Tony Mroczkowski, and Carole Tucker all played important roles in several projects over the years.
Robin Cantor provided excellent customer support for our cryogenic problems.
Conversations with Pieter de Visser and Jochem Baselmans helped to clarify my understanding of quasiparticle dynamics.

Many faculty and students at Columbia contributed to my education in ways both large and small.
The staff of both the Physics and Astrophysics departments deserve my thanks for their cheerful help with many problems.
I learned a lot of physics from the community of graduate students, as we battled problem sets together, and I especially thank Steve Alkire, Derek Araujo, Edgardo Solano-Carillo, Alexa Staley, and Ori Weiner.
I also enjoyed working with several senior group members who have moved on to other positions:
Amber Miller gave me smart career advice;
Michele Limon taught me how to build things the right way;
Glenn Jones was always willing to argue with me, and taught me the value of speed.
Even when collecting and analyzing data alone, I was constantly using laboratory equipment and code that was produced or maintained by current and former group members.
It would take too much space to list all of their contributions, so I will simply thank Max Abitbol, Kristi Bradford, Tanay Bhandarkar, Daniel Chapman, Joy Didier, Mark Greenan, Seth Hillbrand, Bjorn Kjellstrand, Vy Luu, Britt Reichborn-Kjennerud, Brian Smiley, Ross Williamson, and especially Heather McCarrick for her efforts on the detector projects.

I thank my family and friends for helping to keep me sane.
I owe a great debt to my mother, Lucy, and my brother, Ben, for their advice and support during many cross-country phone conversations.
Finally, I thank Charlotte for more than I can say, but most of all for helping me to become both a better graduate student and a better person.
