\section*{Changes}
\setlength{\parindent}{0pt}

\subsection*{Pre-matter}
Added acknowledgements.

\subsection*{Chapter 2}
Minor text edits without content changes.
Added sentence to end of middle paragraph on page 8:
\begin{quote}
Current experiments are searching for this imprint.
\end{quote}

\subsection*{Chapter 3}
Minor text edits without content changes.
Fixed typo in last expression of Equation 3.17.
Adjusted some figure sizes.
Fixed factor of 2 mistake in Figure 3.13 code and adjusted caption accordingly.
Re-wrote final sentence of 3.5.2:
\begin{quote}
It should be possible to measure $\qprecombinationeff$ by combining careful measurements of detector response to thermal quasiparticles with measurements at different illumination levels.
\end{quote}

\subsection*{Chapter 4}
Minor text edits without content changes.
Shrank a few figures that were too large.

\subsection*{Chapter 5}
Minor text edits without content changes.
Added sentence similar to one in published supplement at end of Section 5.2:
\begin{quote}
Because we use this equation as part of the NEP model in the measurements discussed in Section 5.5, we are unable to empirically demonstrate here that the equation given here is correct.
\end{quote}

\subsection*{Chapter 6}
Minor text edits without content changes.

\subsection*{Appendix A}
Corrected Equation A.1: $\qpdensity \rightarrow \qpnumber$.

\subsection*{Appendix B}
Added missing absolute value to Equation B.2.
Fixed missing minus sign in Equation B.30.

\subsection*{References}
Fixed capitalization errors and cleaned up mistakes in reference entries.
No changes to what was cited where.
